FocalGstar

### 2017-06-14 analysis.Rmd
Extended script but not testet

>>>>

```{r weight, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}

d3 <- read.csv("data/w_focal_trued3.csv")
d3global <- read.csv("data/w_focal_falsed3.csv")

mean <- aggregate(d3$Up, by = list(d3$W), mean)
sd <- aggregate(d3$Up, by = list(d3$W), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$W), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$W), sd)
plot(NA, ylab="Up", xlim=c(0,40), ylim=c(0,1), xlab=sprintf("Weight"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
lines(meanG$Group.1, meanG$x, col="blue", lw=4)
legend("topleft", c("Focal","Global") , fill=c("red","blue"))

mean <- aggregate(d3$Down, by = list(d3$W), mean)
sd <- aggregate(d3$Down, by = list(d3$W), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$W), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$W), sd)
plot(NA, ylab="Down", xlim=c(0,40), ylim=c(0,1), xlab=sprintf("Weight"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
lines(meanG$Group.1, meanG$x, col="blue", lw=4)
legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))

```

```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}

d3 <- read.csv("data/a_focal_trued3.csv")
d3global <- read.csv("data/a_focal_falsed3.csv")

mean <- aggregate(d3$Up, by = list(d3$Z), mean)
sd <- aggregate(d3$Up, by = list(d3$Z), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z), sd)
plot(NA, ylab="Up", xlim=c(1,5), ylim=c(0,1), xlab=sprintf("Aggregation"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
lines(meanG$Group.1, meanG$x, col="blue", lw=4)
legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))

mean <- aggregate(d3$Down, by = list(d3$Z), mean)
sd <- aggregate(d3$Down, by = list(d3$Z), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z), sd)
plot(NA, ylab="Down", xlim=c(1,5), ylim=c(0,1), xlab=sprintf("Aggregation"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
lines(meanG$Group.1, meanG$x, col="blue", lw=4)
legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))

```

```{r focal, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}

d3 <- read.csv("data/f_focal_trued3.csv")

mean <- aggregate(d3$Up, by = list(d3$F), mean)
sd <- aggregate(d3$Up, by = list(d3$F), sd)
plot(NA, ylab="Up", xlim=c(0,150), ylim=c(0,1), xlab=sprintf("Focal"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
legend("topleft", c("Focal G*") , fill=c("red"))

mean <- aggregate(d3$Down, by = list(d3$F), mean)
sd <- aggregate(d3$Down, by = list(d3$F), sd)
plot(NA, ylab="Down", xlim=c(0,150), ylim=c(0,1), xlab=sprintf("Focal"))
plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
lines(mean$Group.1, mean$x, col="red", lw=4)
legend("topleft", c("Focal G*") , fill=c("red"))

```
